---
title: "1_ComputeRepeatability"
author: "Ghais ZRIKI, Nicolas RODE"
date: "`r format(Sys.Date(), '%d-%B-%Y')`"
output: 
  html_document: 
    number_sections: yes
    theme: journal
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: no
editor_options: 
  chunk_output_type: console
---

```{r setup, include =FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
devtools::load_all()
```
# Load and check crushing time data
## Load crushing time data
```{r }
## Load count data for each observer
CrushingTime <- tidyr::as_tibble(read.csv(file=file.path(here::here(), "data", "raw_data", "CrushingTime.csv"), header = TRUE, sep = ";"))
CrushingTime <- CrushingTime %>% 
dplyr::mutate(Duration=as.numeric(format(as.POSIXct(Duration,format="%M:%S"),format="%M"))*60+as.numeric(format(as.POSIXct(Duration, format="%M:%S"),format="%S")))

## Mean crush time per fruit
mean(CrushingTime$Duration/CrushingTime$Number_of_fruits)

## Variance of crush time
var(CrushingTime$Duration)/mean(CrushingTime$Number_of_fruits)

## Standard deviation of crush time
sqrt(var(CrushingTime$Duration)/mean(CrushingTime$Number_of_fruits))


```
# Load and check count data
## Load count data 
```{r }
## Load count data for each observer
data <- tidyr::as_tibble(read.csv(file=file.path(here::here(), "data", "raw_data", "Observed_Count_Data.csv"), header = TRUE, sep = ";"))

## Compute bias
data <- data  %>%
  dplyr::mutate(Bias=Obs_No_Larvae-True_No_Larvae)

## Load true counts for each sample
truecounts <- tidyr::as_tibble(read.csv(file=file.path(here::here(), "data", "raw_data", "Expected_Count_Data.csv"), header = TRUE, sep = ";"))

head(data)
#View(data)
dim(data)
#View(truecounts)
head(truecounts)

## Convert as factor
data$Observer_ID <- as.factor(data$Observer_ID)
data$Sample_ID <- as.factor(data$Sample_ID)
data$Incubation <- as.factor(data$Incubation)

## Mean count time per fruit
mean(data$Time_Sec)

## Standard deviation of count time per fruit
sd(data$Time_Sec)

## Mean processing time
mean(CrushingTime$Duration/CrushingTime$Number_of_fruits)+mean(data$Time_Sec)

## Variance in processing time
var(CrushingTime$Duration)/mean(CrushingTime$Number_of_fruits) + var(data$Time_Sec)

## Standard deviation of processing time
sqrt(var(CrushingTime$Duration)/mean(CrushingTime$Number_of_fruits) + var(data$Time_Sec))

```
## Check data
```{r }
## Check that 2 replicates per Observer_ID and Sample_ID
data %>%
  dplyr::select(Observer_ID, Sample_ID) %>% 
  dplyr::group_by(Observer_ID, Sample_ID) %>%
  dplyr::summarise(Count=length(Sample_ID)) %>%
  print(n = 300)
```

## Table 1: sumarize data
```{r}
summary_time <- data %>%
  dplyr::mutate(Counting_error = abs(Obs_No_Larvae - True_No_Larvae), Category_True_No_Larvae=as.factor(cut(True_No_Larvae, breaks=c(0, 5, 10, 15, Inf), labels=c("0-5","5-10","10-15","+15"), right = FALSE))) %>%
  dplyr::select(Previous_Experience, Counting_error, Time_Sec, Incubation, Round, Category_True_No_Larvae) %>%
  dplyr::group_by( Incubation, Previous_Experience, Category_True_No_Larvae) %>%
  dplyr::summarise(Counting_error_mean=mean(Counting_error), Time_Sec_mean=mean(Time_Sec), standard_deviation = sd(Time_Sec), N = length(Time_Sec)) %>% dplyr::mutate(standard_error=standard_deviation/sqrt(N)) %>%
 dplyr::relocate(Category_True_No_Larvae, .before = Incubation) %>%
 dplyr::relocate(standard_error, .before = N) %>%
 dplyr::arrange(Incubation, Previous_Experience, Category_True_No_Larvae) %>% dplyr::mutate(dplyr::across(Counting_error_mean:standard_error, \(x) round(x, digits = 2)))

## Check the levels for Category_True_No_Larvae
levels(summary_time$Category_True_No_Larvae)

## Export table
write.table(x=summary_time, file=file.path(here::here(), "data", "derived_data", "Table1_summary_counting_time.csv"), row.names = FALSE, sep=";")

```
# Compute bias and variance in larval count estimates
```{r }
## Check difference between Obs_No_Larvae and True_No_Larvae
data %>%
  dplyr::mutate(Counting_error = abs(Obs_No_Larvae - True_No_Larvae), Bias = Obs_No_Larvae - True_No_Larvae) %>%   dplyr::select(Previous_Experience, Counting_error, Bias, Time_Sec, Incubation, Round) %>% 
  dplyr::group_by( Incubation, Previous_Experience, Round) %>%
  dplyr::summarise(Counting_error_mean=mean(Counting_error), Bias_mean=mean(Bias),
            Time_Sec_mean=mean(Time_Sec),
            Time_Sec_median=median(Time_Sec)) %>%
            print(n=30)

## Compute Squared Error
Squared_error_data <- data %>%
  dplyr::mutate(Count_error_squared = (Obs_No_Larvae - True_No_Larvae)^2, Bias = Obs_No_Larvae - True_No_Larvae) 
## Compute MSE by sampleID
Squared_error_data %>%
  dplyr::select(Sample_ID, Previous_Experience, Obs_No_Larvae, Count_error_squared, Bias, Incubation, Round) %>% 
  dplyr::group_by(Sample_ID) %>%
  dplyr::summarise(MSE=mean(Count_error_squared), RMSE=sqrt(mean(Count_error_squared)), Bias=mean(Bias), Variance=var(Obs_No_Larvae))

## Compute MSE by sampleID and incubation
MSE_bysampleIDincubation <- data %>%
  dplyr::mutate(Count_error_squared = (Obs_No_Larvae - True_No_Larvae)^2) %>%
  dplyr::select(Sample_ID, Obs_No_Larvae, True_No_Larvae, Count_error_squared, Incubation) %>% 
  dplyr::group_by(Sample_ID, Incubation) %>%
  dplyr::summarise(Mean_Obs_No_Larvae=mean(Obs_No_Larvae), Sum_Obs_No_Larvae=sum(Obs_No_Larvae), True_No_Larvae=mean(True_No_Larvae), Sum_Count_error_squared=sum(Count_error_squared), N=length(Count_error_squared), Var_Obs_No_Larvae=var(Obs_No_Larvae)) %>%
  dplyr::mutate(Bias_Obs_No_Larvae = Mean_Obs_No_Larvae - True_No_Larvae, SquaredBias_Obs_No_Larvae = (Mean_Obs_No_Larvae - True_No_Larvae)^2, Var_Obs_No_Larvae = Var_Obs_No_Larvae*(N-1)/N, MSE = Sum_Count_error_squared/N)%>%
  dplyr::mutate(propBias = SquaredBias_Obs_No_Larvae/MSE) %>%
  print(n = 30)

## Chat that squared bias + variance = MSE
MSE_bysampleIDincubation %>%
  dplyr::select(Sample_ID, Incubation, Bias_Obs_No_Larvae, SquaredBias_Obs_No_Larvae, Var_Obs_No_Larvae, MSE)

## Compute MSE by sampleID and incubation and experience
MSE_bysampleIDincubationExperience <- data %>%
  dplyr::mutate(Count_error_squared = (Obs_No_Larvae - True_No_Larvae)^2) %>%
  dplyr::select(Sample_ID, Previous_Experience, Obs_No_Larvae, True_No_Larvae, Count_error_squared, Incubation) %>% 
  dplyr::group_by(Sample_ID, Incubation, Previous_Experience) %>%
  dplyr::summarise(Mean_Obs_No_Larvae=mean(Obs_No_Larvae), Sum_Obs_No_Larvae=sum(Obs_No_Larvae), True_No_Larvae=mean(True_No_Larvae), Sum_Count_error_squared=sum(Count_error_squared), N=length(Count_error_squared), Var_Obs_No_Larvae=var(Obs_No_Larvae)) %>%
  dplyr::mutate(Bias_Obs_No_Larvae = Mean_Obs_No_Larvae - True_No_Larvae, SquaredBias_Obs_No_Larvae = (Mean_Obs_No_Larvae - True_No_Larvae)^2, Var_Obs_No_Larvae = Var_Obs_No_Larvae*(N-1)/N, MSE = Sum_Count_error_squared/N)%>%
  print(n = 60)

## Chat that squared bias + variance = MSE
MSE_bysampleIDincubationExperience %>%
  dplyr::select(Sample_ID, Incubation, Bias_Obs_No_Larvae, SquaredBias_Obs_No_Larvae, Var_Obs_No_Larvae, MSE)

## Compute MSE by sampleID and incubation and experience and Round
MSEdataRoundExperience <- data %>%
  dplyr::mutate(Count_error_squared = (Obs_No_Larvae - True_No_Larvae)^2) %>%
  dplyr::select(Sample_ID, Round, Previous_Experience, Obs_No_Larvae, True_No_Larvae, Count_error_squared, Incubation) %>% 
  dplyr::group_by(Sample_ID, Round, Incubation, Previous_Experience) %>%
  dplyr::summarise(Mean_Obs_No_Larvae=mean(Obs_No_Larvae), Sum_Obs_No_Larvae=sum(Obs_No_Larvae), True_No_Larvae=mean(True_No_Larvae), Sum_Count_error_squared=sum(Count_error_squared), N=length(Count_error_squared), Var_Obs_No_Larvae=var(Obs_No_Larvae)) %>%
  dplyr::mutate(Bias_Obs_No_Larvae = Mean_Obs_No_Larvae - True_No_Larvae, SquaredBias_Obs_No_Larvae = (Mean_Obs_No_Larvae - True_No_Larvae)^2, Var_Obs_No_Larvae = Var_Obs_No_Larvae*(N-1)/N, MSE = Sum_Count_error_squared/N)%>%
  print(n = 60)

## Chat that squared bias + variance = MSE
MSEdataRoundExperience %>%
  dplyr::select(Sample_ID, Incubation, Bias_Obs_No_Larvae, SquaredBias_Obs_No_Larvae, Var_Obs_No_Larvae, MSE)

```

# Analyses
## Time for counting larvae
```{r }
## Step1:Complete model
m0 <- lme4::lmer(log(Time_Sec)~Incubation*True_No_Larvae+Previous_Experience+Round+(1|Sample_ID)+(1|Observer_ID), data=data)
summary(m0)

## -Incubation*True_No_Larvae
m1 <- lme4::lmer(log(Time_Sec)~Incubation+True_No_Larvae+Round+Previous_Experience+(1|Sample_ID)+(1|Observer_ID), data=data)

anova(m0, m1, test="Chisq")

## -Previous_Experience
m2 <- lme4::lmer(log(Time_Sec)~Incubation*True_No_Larvae+Round+(1|Sample_ID)+(1|Observer_ID), data=data)
summary(m2)

anova(m0, m2, test="Chisq")

## -Round
m3 <- lme4::lmer(log(Time_Sec)~Incubation*True_No_Larvae+Previous_Experience+(1|Sample_ID)+(1|Observer_ID), data=data)

anova(m0, m3, test="Chisq")


## Step2: We continue with the model with highest P-value (m1) and test for each remaining fixed effects

## -Previous_Experience
m4 <- lme4::lmer(log(Time_Sec)~Incubation+True_No_Larvae+Round+(1|Sample_ID)+(1|Observer_ID), data=data)
anova(m1, m4, test="Chisq")

## -Round
m5 <- lme4::lmer(log(Time_Sec)~Incubation+True_No_Larvae+Previous_Experience+(1|Sample_ID)+(1|Observer_ID), data=data)
anova(m1, m5, test="Chisq")

## -Incubation
m6 <- lme4::lmer(log(Time_Sec)~True_No_Larvae+Round+Previous_Experience+(1|Sample_ID)+(1|Observer_ID), data=data)
anova(m1, m6, test="Chisq")

## -True_No_Larvae
m7 <- lme4::lmer(log(Time_Sec)~Incubation+Round+Previous_Experience+(1|Sample_ID)+(1|Observer_ID), data=data)
summary(m7)
anova(m1, m7, test="Chisq")

## Step3: We continue with the model with highest P-value (m6) and test for each remaining fixed effects

## -True_No_Larvae
m8 <- lme4::lmer(log(Time_Sec)~Round+Previous_Experience+(1|Sample_ID)+(1|Observer_ID), data=data)
anova(m6, m8, test="Chisq")

## -Round
m9 <- lme4::lmer(log(Time_Sec)~True_No_Larvae+Previous_Experience+(1|Sample_ID)+(1|Observer_ID), data=data)
anova(m6, m9, test="Chisq")

## -Previous_Experience
m10 <- lme4::lmer(log(Time_Sec)~True_No_Larvae+Round+(1|Sample_ID)+(1|Observer_ID), data=data)
anova(m6, m10, test="Chisq")

## Step3: We continue with the model with highest P-value (m10) and test for each remaining fixed effects

## -True_No_Larvae
m11 <- lme4::lmer(log(Time_Sec)~Round+(1|Sample_ID)+(1|Observer_ID), data=data)
anova(m10, m11, test="Chisq")

## -Round
m12 <- lme4::lmer(log(Time_Sec)~True_No_Larvae+(1|Sample_ID)+(1|Observer_ID), data=data)
anova(m10, m12, test="Chisq")

## step4: Compute the final p-values of effect that have been removed
## +Incubation
m13 <- lme4::lmer(log(Time_Sec)~Incubation*factor(True_No_Larvae)+Round+(1|Sample_ID)+(1|Observer_ID), data=data)
summary(m13)
anova(m13, m10, test="Chisq")

## Check residuals
ggplot() +
  aes(x=residuals(m10))+ 
  geom_histogram(binwidth=0.1)
```
## Accuracy (bias)
```{r }
## Mixed model
## Step1:Complete model
m0 <- lme4::lmer(Bias~Incubation*True_No_Larvae+Previous_Experience+Round+(1|Sample_ID)+(1|Observer_ID), data=data)
summary(m0)

## -Incubation*True_No_Larvae
m1 <- lme4::lmer(Bias~Incubation+True_No_Larvae+Previous_Experience+Round+(1|Sample_ID)+(1|Observer_ID), data=data)

anova(m0, m1, test="Chisq")

## -Previous_Experience
m2 <- lme4::lmer(Bias~Incubation*True_No_Larvae+Round+(1|Sample_ID)+(1|Observer_ID), data=data)
anova(m0, m2, test="Chisq")


## -Round
m3 <- lme4::lmer(Bias~Incubation*True_No_Larvae+Previous_Experience+(1|Sample_ID)+(1|Observer_ID), data=data)
summary(m3)
anova(m0, m3, test="Chisq")


```

## Precision (standard deviation)
```{r }
```
## Analyse repeatability
```{r }
## Mixed model
m0 <- lme4::lmer(log(Obs_No_Larvae+1)~1+(1|Sample_ID)+(1|Observer_ID), data=data, REML = TRUE)
summary(m0)

## -(1|Observer_ID)
m1 <- lme4::lmer(log(Obs_No_Larvae+1)~1+(1|Sample_ID), data=data, REML = TRUE)
summary(m1)
anova(m0, m1, test="Chisq")

## Extract variance components
VAR <- as.data.frame(lme4::VarCorr(m0))$vcov

## Compute repeatability among observers
RepeatabilityAmong <- VAR[1]/sum(VAR)
## Compute repeatability within observers
RepeatabilityWithin <- VAR[1]/sum(VAR[c(1, 3)])
```

# Plots
## Time for counting larvae

```{r }
## Histogram with time
ggplot(data, aes(x=log(Time_Sec))) + 
  geom_histogram(binwidth=1)

siz <- 10
## Time used for counting as a function of number of larvae
p2A <- data %>%
  dplyr::mutate(Category_True_No_Larvae=cut(True_No_Larvae, breaks=c(0, 1, 6, Inf), labels=c("0","1-5","+5"), right = FALSE)) %>%
  dplyr::select(Category_True_No_Larvae, Incubation, Time_Sec) %>%
  ggplot(aes(x=Category_True_No_Larvae,  y=Time_Sec, color=Incubation)) + geom_boxplot() + xlab("Number of larvae") + ylab("Time for counting larvae (sec.)") + scale_color_discrete(name = "48h-incubation") + theme(text = element_text(size = siz))

p2A

```
## Accuracy (bias)
```{r }
p2B <- MSE_bysampleIDincubation %>%
  dplyr::mutate(Category_True_No_Larvae=cut(True_No_Larvae, breaks=c(0, 1, 6, Inf), labels=c("0","1-5","+5"), right = FALSE)) %>%
  ggplot(aes(x=Category_True_No_Larvae, y=Bias_Obs_No_Larvae, color=Incubation)) + geom_boxplot() +
  xlab("Number of larvae") + ylab("Bias in larval count estimates") + scale_color_discrete(name = "48h-incubation") + theme(text = element_text(size = siz))
p2B
```

## Precision (stadnard deviation)
```{r }

p2C <- MSE_bysampleIDincubation %>%
  dplyr::mutate(Category_True_No_Larvae=cut(True_No_Larvae, breaks=c(0, 1, 6, Inf), labels=c("0","1-5","+5"), right = FALSE)) %>%
  ggplot(aes(x=Category_True_No_Larvae, y=sqrt(Var_Obs_No_Larvae), color=Incubation)) + geom_boxplot() +
  xlab("Number of larvae") + ylab("Standard deviation in\n larval count estimates") + scale_color_discrete(name = "48h-incubation") + ylim(0, 7) + theme(text = element_text(size = siz))
p2C


figure <- ggpubr::ggarrange(p2A, p2B, p2C,
                    labels = c("A", "B", "C"),
                    ncol = 1, nrow = 3, common.legend = TRUE, legend = "bottom")

title_plot <- "Fig2_TimeBiasSDbyNumLarvaeandIncubation.png"
cowplot::save_plot(file =here::here("plots", title_plot),
                 figure, base_height = 21/cm(1),
                  base_width = 10/cm(1), dpi = 1200)


```

# Supp. plots
```{r }


## Relationship between expected and observed number of larvae
pS1 <- data %>%
  dplyr::select(Obs_No_Larvae, True_No_Larvae, Incubation, Round) %>%
  ggplot(aes(x=True_No_Larvae, Obs_No_Larvae, color=Incubation)) + geom_point() + xlim(0, 35) + ylim(0, 35) + geom_abline(intercept = 0, slope = 1)+ xlab("Expected number of larvae") + ylab("Observed number of larvae") + scale_color_discrete(name = "48h-incubation")
pS1

title_plot <- "FigS1_Observed_Expected_No_Larvae.png"
cowplot::save_plot(file =here::here("plots", title_plot),
                 pS1, base_height = 10/cm(1),
                  base_width = 12.5/cm(1), dpi = 1200)


siz <- 10
## Relationship between bias and expected number of larvae
pS2A <- data %>%
  ggplot(aes(x=True_No_Larvae, y=Time_Sec, color=Incubation)) + geom_point() + xlim(0, 35) + ylim(0, 125) + xlab("Number of larvae") + ylab("Time for counting larvae (sec.)") + scale_color_discrete(name = "48h-incubation") + theme(text = element_text(size = siz))
pS2A


## Relationship between bias and expected number of larvae
pS2B <- data %>%
  ggplot(aes(x=True_No_Larvae, y=Obs_No_Larvae-True_No_Larvae, color=Incubation)) + geom_point() + xlim(0, 35) + ylim(-30, 10) + geom_abline(intercept = 0.47, slope = -0.47, linetype=3)+ xlab("Number of larvae") + ylab("Bias in larval count estimates") + scale_color_discrete(name = "48h-incubation") + theme(text = element_text(size = siz))
pS2B


## Relationship between variance and expected number of larvae
pS2C <- MSE_bysampleIDincubation %>%
  ggplot(aes(x=True_No_Larvae, y=sqrt(Var_Obs_No_Larvae), color=Incubation)) + geom_point() + xlim(0, 35) + ylim(0, 7) + xlab("Number of larvae") + ylab("Standard deviation in\n larval count estimates") + scale_color_discrete(name = "48h-incubation") + theme(text = element_text(size = siz))
pS2C

figure <- ggpubr::ggarrange(pS2A, pS2B, pS2C,
                    labels = c("A", "B", "C"),
                    ncol = 1, nrow = 3, common.legend = TRUE, legend = "bottom")

title_plot <- "FigS2_TimeBiasSDbyNumLarvaeandIncubation.png"
cowplot::save_plot(file =here::here("plots", title_plot),
                 figure, base_height = 21/cm(1),
                  base_width = 10/cm(1), dpi = 1200)



## Space between replicates
x <- 0.25
## Relationship between bias and expected number of larvae
pS3A <- data %>%
  dplyr::mutate(Replicate=as.factor(dplyr::if_else(Round=="A", 1, 2))) %>%
  dplyr::mutate(True_No_Larvae=dplyr::if_else(Round=="A", True_No_Larvae-x, True_No_Larvae+x)) %>%
  ggplot(aes(x=True_No_Larvae, y=Time_Sec, color=Round)) + geom_point() + xlim(-1, 35) + ylim(0, 125) + xlab("Number of larvae") + ylab("Time for counting larvae (sec.)") + scale_color_discrete(name = "Replicate") + theme(text = element_text(size = siz))
pS3A


## Relationship between bias and expected number of larvae
pS3B <- data %>%
  dplyr::mutate(Replicate=as.factor(dplyr::if_else(Round=="A", 1, 2))) %>%
  dplyr::mutate(True_No_Larvae=dplyr::if_else(Round=="A", True_No_Larvae-x, True_No_Larvae+x)) %>%
  ggplot(aes(x=True_No_Larvae, y=Obs_No_Larvae-True_No_Larvae, color=Replicate)) + geom_point() + xlim(-1, 35) + ylim(-32, 10) + xlab("Number of larvae") + ylab("Bias in larval count estimates") + scale_color_discrete(name = "Replicate") + theme(text = element_text(size = siz))
pS3B


## Relationship between variance and expected number of larvae
pS3C <- MSEdataRoundExperience %>%
  dplyr::mutate(Replicate=as.factor(dplyr::if_else(Round=="A", 1, 2))) %>%
  dplyr::mutate(True_No_Larvae=dplyr::if_else(Round=="A", True_No_Larvae-x, True_No_Larvae+x)) %>%
  ggplot(aes(x=True_No_Larvae, y=sqrt(Var_Obs_No_Larvae), color=Replicate)) + geom_point() + xlim(-1, 35) + ylim(0, 10) + xlab("Number of larvae") + ylab("Standard deviation in\n larval count estimates") + scale_color_discrete(name = "Replicate") + theme(text = element_text(size = siz))
pS3C

figure <- ggpubr::ggarrange(pS3A, pS3B, pS3C,
                    labels = c("A", "B", "C"),
                    ncol = 1, nrow = 3, common.legend = TRUE, legend = "bottom")

title_plot <- "FigS3_TimeBiasSDbyNumLarvaeandReplicate.png"
cowplot::save_plot(file =here::here("plots", title_plot),
                 figure, base_height = 21/cm(1),
                  base_width = 10/cm(1), dpi = 1200)




```

# Test for differences in the number of larvae between incubated and non incubated samples
```{r}
## Check for an absence of differences in the number of larvae between incubated and non incubated samples

## Check the mean number of larvae for samples with 48h of incubation or not
truecounts %>%
  dplyr::group_by(Incubation) %>%
  dplyr::summarise(True_No_Larvae_mean=mean(True_No_Larvae), True_No_Larvae_median=median(True_No_Larvae))

m <- glm(True_No_Larvae~Incubation, data=truecounts, family="poisson")
summary(m)

```
