---
title: "1_ComputeRepeatability"
author: "Ghais ZRIKI, Nicolas RODE"
date: "`r format(Sys.Date(), '%d-%B-%Y')`"
output: 
  html_document: 
    number_sections: yes
    theme: journal
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: no
editor_options: 
  chunk_output_type: console
---

```{r setup, include =FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
devtools::load_all()
```
# Load and check crushing time data
## Load crushing time data
```{r }
## Load count data for each observer
CrushingTime <- tidyr::as_tibble(read.csv(file=file.path(here::here(), "data", "raw_data", "CrushingTime.csv"), header = TRUE, sep = ";"))
CrushingTime <- CrushingTime %>% 
dplyr::mutate(Duration=as.numeric(format(as.POSIXct(Duration,format="%M:%S"),format="%M"))*60+as.numeric(format(as.POSIXct(Duration, format="%M:%S"),format="%S")))

## Mean crush time per fruit
mean(CrushingTime$Duration/CrushingTime$Number_of_fruits)

## Variance of crush time
var(CrushingTime$Duration)/mean(CrushingTime$Number_of_fruits)

## Standard deviation of crush time
sqrt(var(CrushingTime$Duration)/mean(CrushingTime$Number_of_fruits))


```
# Load and check count data
## Load count data 
```{r }
## Load count data for each observer
data <- tidyr::as_tibble(read.csv(file=file.path(here::here(), "data", "raw_data", "Observed_Count_Data.csv"), header = TRUE, sep = ";"))

## Compute bias and rename round column and convert as factor
data <- data  %>%
  dplyr::mutate(Bias=Obs_No_Larvae-True_No_Larvae)  %>%
  dplyr::mutate(Replicate=as.factor(dplyr::if_else(Round=="A", 1, 2))) %>%
  dplyr::mutate(Observer_ID=as.factor(Observer_ID), Sample_ID=as.factor(Sample_ID), Incubation=as.factor(Incubation))
  
## Load true counts for each sample
truecounts <- tidyr::as_tibble(read.csv(file=file.path(here::here(), "data", "raw_data", "Expected_Count_Data.csv"), header = TRUE, sep = ";"))

head(data)
#View(data)
dim(data)
#View(truecounts)
head(truecounts)

## Mean count time per fruit
mean(data$Time_Sec)

## Standard deviation of count time per fruit
sd(data$Time_Sec)

## Mean processing time
mean(CrushingTime$Duration/CrushingTime$Number_of_fruits)+mean(data$Time_Sec)

## Variance in processing time
var(CrushingTime$Duration)/mean(CrushingTime$Number_of_fruits) + var(data$Time_Sec)

## Standard deviation of processing time
sqrt(var(CrushingTime$Duration)/mean(CrushingTime$Number_of_fruits) + var(data$Time_Sec))

```
## Check data
```{r }
## Check that 2 replicates per Observer_ID and Sample_ID
data %>%
  dplyr::select(Observer_ID, Sample_ID) %>% 
  dplyr::group_by(Observer_ID, Sample_ID) %>%
  dplyr::summarise(Count=length(Sample_ID)) %>%
  print(n = 300)
```

## Table 1: sumarize data
```{r}
summary_time <- data %>%
  dplyr::mutate(Counting_error = abs(Obs_No_Larvae - True_No_Larvae), Category_True_No_Larvae=as.factor(cut(True_No_Larvae, breaks=c(0, 6, 10, 15, Inf), labels=c("0-5","5-10","10-15","+15"), right = FALSE))) %>%
  dplyr::select(Previous_Experience, Counting_error, Time_Sec, Incubation, Round, Category_True_No_Larvae) %>%
  dplyr::group_by( Incubation, Previous_Experience, Category_True_No_Larvae) %>%
  dplyr::summarise(Counting_error_mean=mean(Counting_error), Time_Sec_mean=mean(Time_Sec), standard_deviation = sd(Time_Sec), N = length(Time_Sec)) %>% dplyr::mutate(standard_error=standard_deviation/sqrt(N)) %>%
 dplyr::relocate(Category_True_No_Larvae, .before = Incubation) %>%
 dplyr::relocate(standard_error, .before = N) %>%
 dplyr::arrange(Incubation, Previous_Experience, Category_True_No_Larvae) %>% dplyr::mutate(dplyr::across(Counting_error_mean:standard_error, \(x) round(x, digits = 2)))

## Check the levels for Category_True_No_Larvae
levels(summary_time$Category_True_No_Larvae)

## Export table
write.table(x=summary_time, file=file.path(here::here(), "data", "derived_data", "Table1_summary_counting_time.csv"), row.names = FALSE, sep=";")

```
# Compute MSE, bias and variance in larval count estimates
## By sampleID
```{r }

## Compute Squared Error
data <- data %>%
  dplyr::mutate(Count_error_squared = (Obs_No_Larvae - True_No_Larvae)^2, Obs_bias = Obs_No_Larvae - True_No_Larvae) 

## Compute MSE by sampleID
data %>%
  dplyr::select(Sample_ID, Previous_Experience, Obs_No_Larvae, True_No_Larvae, Count_error_squared, Bias, Incubation, Round) %>% 
  dplyr::group_by(Sample_ID) %>%
  dplyr::summarise(MSE=mean(Count_error_squared), RMSE=sqrt(mean(Count_error_squared)), Bias=mean(Obs_No_Larvae) - mean(True_No_Larvae), N=length(Obs_No_Larvae), Variance=sd(Obs_No_Larvae)^2, MSE2=Bias^2+Variance*(N-1)/N) ## Check that the MSE equals the squared of the mean bias + the unbisaised sample variance https://en.wikipedia.org/wiki/Variance#Sample_variance

```
## Compute MSE, bias and variance by sampleID and incubation and replicate
```{r }

MSEdataSample_IDReplicateIncubation <- data %>%
  dplyr::select(Sample_ID, Replicate, Time_Sec, Obs_No_Larvae, True_No_Larvae, Count_error_squared, Incubation) %>% 
  dplyr::group_by(Sample_ID, Replicate, Incubation) %>%
  dplyr::summarise(Mean_Time_Sec=mean(Time_Sec), Mean_Obs_No_Larvae=mean(Obs_No_Larvae), Sum_Obs_No_Larvae=sum(Obs_No_Larvae), True_No_Larvae=mean(True_No_Larvae), Sum_Count_error_squared=sum(Count_error_squared), N=length(Count_error_squared), Var_Obs_No_Larvae=var(Obs_No_Larvae)) %>%
  dplyr::mutate(Bias_Obs_No_Larvae = Mean_Obs_No_Larvae - True_No_Larvae, Var_Obs_No_Larvae = Var_Obs_No_Larvae*(N-1)/N, SD_Obs_No_Larvae=sqrt(Var_Obs_No_Larvae), MSE = Sum_Count_error_squared/N, MSE2=Bias_Obs_No_Larvae^2 + Var_Obs_No_Larvae) %>% ## Check that the MSE equals the squared of the mean bias + the unbiased sample variance https://en.wikipedia.org/wiki/Variance#Sample_variance
  dplyr::mutate(propBias = Bias_Obs_No_Larvae^2/MSE) %>%
  print(n = 60)


```
## Compute MSE, bias and variance by sampleID and incubation and replicate and experience
```{r }

MSEdataSample_IDReplicateIncubationExperience <- data %>%
  dplyr::select(Sample_ID, Replicate, Time_Sec, Obs_No_Larvae, True_No_Larvae, Count_error_squared, Incubation, Previous_Experience) %>% 
  dplyr::group_by(Sample_ID, Replicate, Incubation, Previous_Experience) %>%
  dplyr::summarise(Mean_Time_Sec=mean(Time_Sec), Mean_Obs_No_Larvae=mean(Obs_No_Larvae), Sum_Obs_No_Larvae=sum(Obs_No_Larvae), True_No_Larvae=mean(True_No_Larvae), Sum_Count_error_squared=sum(Count_error_squared), N=length(Count_error_squared), Var_Obs_No_Larvae=var(Obs_No_Larvae)) %>%
  dplyr::mutate(Bias_Obs_No_Larvae = Mean_Obs_No_Larvae - True_No_Larvae, Var_Obs_No_Larvae = Var_Obs_No_Larvae*(N-1)/N, SD_Obs_No_Larvae=sqrt(Var_Obs_No_Larvae), MSE = Sum_Count_error_squared/N, MSE2=Bias_Obs_No_Larvae^2 + Var_Obs_No_Larvae) %>% ## Check that the MSE equals the squared of the mean bias + the unbiased sample variance https://en.wikipedia.org/wiki/Variance#Sample_variance
  dplyr::mutate(propBias = Bias_Obs_No_Larvae^2/MSE) %>%
  print(n = 60)


```
## Compute rate of FalsePositive and FalseNegative
```{r }

FalsePositive <- data %>%
  dplyr::select(Observer_ID, Replicate, Time_Sec, Obs_No_Larvae, True_No_Larvae, Incubation) %>%
  dplyr::filter(True_No_Larvae==0) %>% 
  dplyr::summarise(FR=mean(dplyr::if_else(Obs_No_Larvae==0, 0, 1)))

FalseNegative <- data %>%
  dplyr::select(Observer_ID, Replicate, Time_Sec, Obs_No_Larvae, True_No_Larvae, Incubation) %>%
  dplyr::filter(True_No_Larvae>0) %>%
  dplyr::summarise(FN=mean(dplyr::if_else(Obs_No_Larvae==0, 1, 0)))

FalseNegative <- data %>%
  dplyr::select(Observer_ID, Replicate, Time_Sec, Obs_No_Larvae, True_No_Larvae, Incubation) %>%
  dplyr::filter(True_No_Larvae>0) %>%
  dplyr::group_by(Observer_ID) %>% 
  dplyr::summarise(FN=mean(dplyr::if_else(Obs_No_Larvae==0, 1, 0)))

```
# Analyses
## Time for counting larvae
```{r }
## Step1:Complete model
m0 <- lme4::lmer(log(Time_Sec)~Incubation*True_No_Larvae+Previous_Experience+Replicate+(1|Sample_ID)+(1|Observer_ID), data=data)
summary(m0)

## -Incubation*True_No_Larvae
m1 <- lme4::lmer(log(Time_Sec)~Incubation+True_No_Larvae+Replicate+Previous_Experience+(1|Sample_ID)+(1|Observer_ID), data=data)

anova(m0, m1, test="Chisq")

## -Previous_Experience
m2 <- lme4::lmer(log(Time_Sec)~Incubation*True_No_Larvae+Replicate+(1|Sample_ID)+(1|Observer_ID), data=data)
summary(m2)
anova(m0, m2, test="Chisq")

## -Replicate
m3 <- lme4::lmer(log(Time_Sec)~Incubation*True_No_Larvae+Previous_Experience+(1|Sample_ID)+(1|Observer_ID), data=data)
anova(m0, m3, test="Chisq")


## Step2: We continue with the model with highest P-value (m1) and test for each remaining fixed effects

## -Previous_Experience
m4 <- lme4::lmer(log(Time_Sec)~Incubation+True_No_Larvae+Replicate+(1|Sample_ID)+(1|Observer_ID), data=data)
anova(m1, m4, test="Chisq")

## -Replicate
m5 <- lme4::lmer(log(Time_Sec)~Incubation+True_No_Larvae+Previous_Experience+(1|Sample_ID)+(1|Observer_ID), data=data)
anova(m1, m5, test="Chisq")

## -Incubation
m6 <- lme4::lmer(log(Time_Sec)~True_No_Larvae+Replicate+Previous_Experience+(1|Sample_ID)+(1|Observer_ID), data=data)
anova(m1, m6, test="Chisq")

## -True_No_Larvae
m7 <- lme4::lmer(log(Time_Sec)~Incubation+Replicate+Previous_Experience+(1|Sample_ID)+(1|Observer_ID), data=data)
summary(m7)
anova(m1, m7, test="Chisq")

## Step3: We continue with the model with highest P-value (m6) and test for each remaining fixed effects

## -True_No_Larvae
m8 <- lme4::lmer(log(Time_Sec)~Replicate+Previous_Experience+(1|Sample_ID)+(1|Observer_ID), data=data)
anova(m6, m8, test="Chisq")

## -Replicate
m9 <- lme4::lmer(log(Time_Sec)~True_No_Larvae+Previous_Experience+(1|Sample_ID)+(1|Observer_ID), data=data)
anova(m6, m9, test="Chisq")

## -Previous_Experience (Best model)
m10 <- lme4::lmer(log(Time_Sec)~True_No_Larvae+Replicate+(1|Sample_ID)+(1|Observer_ID), data=data)
anova(m6, m10, test="Chisq")
summary(m10)

## Step3: We continue with the model with highest P-value (m10) and test for each remaining fixed effects

## -True_No_Larvae
m11 <- lme4::lmer(log(Time_Sec)~Replicate+(1|Sample_ID)+(1|Observer_ID), data=data)
anova(m10, m11, test="Chisq")

## -Replicate
m12 <- lme4::lmer(log(Time_Sec)~True_No_Larvae+(1|Sample_ID)+(1|Observer_ID), data=data)
anova(m10, m12, test="Chisq")

## step4: Compute the final p-values of effect that have been removed
## +Incubation
m13 <- lme4::lmer(log(Time_Sec)~Incubation + True_No_Larvae+Replicate+(1|Sample_ID)+(1|Observer_ID), data=data)
summary(m13)
anova(m13, m10, test="Chisq")

## Check residuals
ggplot() +
  aes(x=residuals(m10))+ 
  geom_histogram(binwidth=0.1)

## Extract coefficient from the best model
coefTime <- lme4::fixef(m10)

## Function to for the fitted curve
fitTimeReplicate1 <- function(x){
  return(exp(coefTime[1]+coefTime[2]*x))
}
fitTimeReplicate2 <- function(x){
  return(exp(coefTime[1]+coefTime[3]+coefTime[2]*x))
}

```

## Accuracy (bias)
```{r }
## Mixed model
## Step1:Complete model
m0 <- lme4::lmer(Bias_Obs_No_Larvae~Incubation*True_No_Larvae+Previous_Experience+Replicate+Mean_Time_Sec+(1|Sample_ID), data=MSEdataSample_IDReplicateIncubationExperience)
summary(m0)

## -Incubation:True_No_Larvae
m1 <- lme4::lmer(Bias_Obs_No_Larvae~Incubation+True_No_Larvae+Previous_Experience+Replicate+Mean_Time_Sec+(1|Sample_ID), data=MSEdataSample_IDReplicateIncubationExperience)
anova(m0, m1, test="Chisq")

## -Previous_Experience (best model)
m2 <- lme4::lmer(Bias_Obs_No_Larvae~Incubation*True_No_Larvae+Replicate+Mean_Time_Sec+(1|Sample_ID), data=MSEdataSample_IDReplicateIncubationExperience)
summary(m2)
anova(m0, m2, test="Chisq")

## -Replicate
m3 <- lme4::lmer(Bias_Obs_No_Larvae~Incubation*True_No_Larvae+Previous_Experience+Mean_Time_Sec+(1|Sample_ID), data=MSEdataSample_IDReplicateIncubationExperience)
anova(m0, m3, test="Chisq")

## -Time_Sec
m4 <- lme4::lmer(Bias_Obs_No_Larvae~Incubation*True_No_Larvae+Previous_Experience+Replicate+(1|Sample_ID), data=MSEdataSample_IDReplicateIncubationExperience)
anova(m0, m4, test="Chisq")

## Step2: We continue with the model with highest P-value (m2) and test for each remaining fixed effects

## -Incubation:True_No_Larvae
m5 <- lme4::lmer(Bias_Obs_No_Larvae~Incubation+True_No_Larvae+Replicate+Mean_Time_Sec+(1|Sample_ID), data=MSEdataSample_IDReplicateIncubationExperience)
anova(m2, m5, test="Chisq")

## -Replicate
m6 <- lme4::lmer(Bias_Obs_No_Larvae~Incubation*True_No_Larvae+Mean_Time_Sec+(1|Sample_ID), data=MSEdataSample_IDReplicateIncubationExperience)
anova(m2, m6, test="Chisq")

## -Time_Sec
m7 <- lme4::lmer(Bias_Obs_No_Larvae~Incubation*True_No_Larvae+Replicate+(1|Sample_ID), data=MSEdataSample_IDReplicateIncubationExperience)
anova(m2, m7, test="Chisq")



## Check that the interaction remains when removing the non incubated sample with a high number of larvae
m2 <- lme4::lmer(Bias_Obs_No_Larvae~Incubation*True_No_Larvae+Replicate+Mean_Time_Sec+(1|Sample_ID), data=MSEdataSample_IDReplicateIncubationExperience[MSEdataSample_IDReplicateIncubationExperience$True_No_Larvae<30,])
m5 <- lme4::lmer(Bias_Obs_No_Larvae~Incubation+True_No_Larvae+Replicate+Mean_Time_Sec+(1|Sample_ID), data=MSEdataSample_IDReplicateIncubationExperience[MSEdataSample_IDReplicateIncubationExperience$True_No_Larvae<30,])
anova(m2, m5, test="Chisq")

## Check normality of residuals
dplyr::tibble(res = residuals(m2)) %>%
  ggplot(aes(x=res)) + 
  geom_histogram(binwidth=0.5)

## Extract coefficient from the best model
coefBias<- lme4::fixef(m2)

## Function to for the fitted curve
fitBiasIncubationYes <- function(x){
  return(coefBias[1] + coefBias[2] + coefBias[3]*x + coefBias[5]*mean(MSEdataSample_IDReplicateIncubationExperience$Mean_Time_Sec) + coefBias[6]*x)
}
fitBiasIncubationNo <- function(x){
  return(coefBias[1] + coefBias[3]*x + coefBias[5]*mean(MSEdataSample_IDReplicateIncubationExperience$Mean_Time_Sec))
}

fitBiasIncubationYesReplicate2 <- function(x){
  return(coefBias[1] + coefBias[2] + coefBias[3]*x + coefBias[4] + coefBias[5]*mean(MSEdataSample_IDReplicateIncubationExperience$Mean_Time_Sec) + coefBias[6]*x)
}
fitBiasIncubationNoReplicate2 <- function(x){
  return(coefBias[1] + coefBias[3]*x + coefBias[4] + coefBias[5]*mean(MSEdataSample_IDReplicateIncubationExperience$Mean_Time_Sec))
}
```
## Precision (standard deviation)
```{r }
## Mixed model
## Step1:Complete model
m0 <- lme4::lmer(SD_Obs_No_Larvae~Incubation*True_No_Larvae+Previous_Experience+Replicate+Mean_Time_Sec+(1|Sample_ID), data=MSEdataSample_IDReplicateIncubationExperience)
summary(m0)

## -Incubation:True_No_Larvae
m1 <- lme4::lmer(SD_Obs_No_Larvae~Incubation+True_No_Larvae+Previous_Experience+Replicate+Mean_Time_Sec+(1|Sample_ID), data=MSEdataSample_IDReplicateIncubationExperience)
anova(m0, m1, test="Chisq")

## -Previous_Experience
m2 <- lme4::lmer(SD_Obs_No_Larvae~Incubation*True_No_Larvae+Replicate+Mean_Time_Sec+(1|Sample_ID), data=MSEdataSample_IDReplicateIncubationExperience)
summary(m2)
anova(m0, m2, test="Chisq")

## -Replicate
m3 <- lme4::lmer(SD_Obs_No_Larvae~Incubation*True_No_Larvae+Previous_Experience+Mean_Time_Sec+(1|Sample_ID), data=MSEdataSample_IDReplicateIncubationExperience)
anova(m0, m3, test="Chisq")

## -Time_Sec
m4 <- lme4::lmer(SD_Obs_No_Larvae~Incubation*True_No_Larvae+Previous_Experience+Replicate+(1|Sample_ID), data=MSEdataSample_IDReplicateIncubationExperience)
anova(m0, m4, test="Chisq")

## Step2: We continue with the model with highest P-value (m2) and test for each remaining fixed effects

## -Incubation:True_No_Larvae
m5 <- lme4::lmer(SD_Obs_No_Larvae~Incubation+True_No_Larvae+Replicate+Mean_Time_Sec+(1|Sample_ID), data=MSEdataSample_IDReplicateIncubationExperience)
anova(m2, m5, test="Chisq")

## -Replicate
m6 <- lme4::lmer(SD_Obs_No_Larvae~Incubation*True_No_Larvae+Mean_Time_Sec+(1|Sample_ID), data=MSEdataSample_IDReplicateIncubationExperience)
anova(m2, m6, test="Chisq")

## -Time_Sec
m7 <- lme4::lmer(SD_Obs_No_Larvae~Incubation*True_No_Larvae+Replicate+(1|Sample_ID), data=MSEdataSample_IDReplicateIncubationExperience)
anova(m2, m7, test="Chisq")

## Step3: We continue with the model with highest P-value (m5) and test for each remaining fixed effects
## -Incubation  (best model)
m8 <- lme4::lmer(SD_Obs_No_Larvae~True_No_Larvae+Replicate+Mean_Time_Sec+(1|Sample_ID), data=MSEdataSample_IDReplicateIncubationExperience)
summary(m8)
anova(m5, m8, test="Chisq")

## -True_No_Larvae
m9 <- lme4::lmer(SD_Obs_No_Larvae~Incubation+Replicate+Mean_Time_Sec+(1|Sample_ID), data=MSEdataSample_IDReplicateIncubationExperience)
anova(m5, m9, test="Chisq")

## -Replicate
m10 <- lme4::lmer(SD_Obs_No_Larvae~Incubation+True_No_Larvae+Mean_Time_Sec+(1|Sample_ID), data=MSEdataSample_IDReplicateIncubationExperience)
anova(m5, m10, test="Chisq")

## -Mean_Time_Sec
m11 <- lme4::lmer(SD_Obs_No_Larvae~Incubation+True_No_Larvae+Replicate+(1|Sample_ID), data=MSEdataSample_IDReplicateIncubationExperience)
anova(m5, m11, test="Chisq")

## Step4: We continue with the model with highest P-value (m8) and test for each remaining fixed effects
## -True_No_Larvae
m12 <- lme4::lmer(SD_Obs_No_Larvae~Replicate+Mean_Time_Sec+(1|Sample_ID), data=MSEdataSample_IDReplicateIncubationExperience)
anova(m8, m12, test="Chisq")

## -Replicate
m13 <- lme4::lmer(SD_Obs_No_Larvae~True_No_Larvae+Mean_Time_Sec+(1|Sample_ID), data=MSEdataSample_IDReplicateIncubationExperience)
anova(m8, m13, test="Chisq")

## -Mean_Time_Sec
m14 <- lme4::lmer(SD_Obs_No_Larvae~True_No_Larvae+Replicate+(1|Sample_ID), data=MSEdataSample_IDReplicateIncubationExperience)
anova(m8, m14, test="Chisq")

## + Previous_Experience
m15 <- lme4::lmer(SD_Obs_No_Larvae~True_No_Larvae+Replicate+Mean_Time_Sec+Previous_Experience+(1|Sample_ID), data=MSEdataSample_IDReplicateIncubationExperience)
summary(m15)
anova(m15, m8, test="Chisq")



## Check normality of residuals
dplyr::tibble(res = residuals(m8)) %>%
  ggplot(aes(x=res)) + 
  geom_histogram(binwidth=0.5)

## Extract coefficient from the best model
coefPrecision<- lme4::fixef(m8)

## Function to for the fitted curve

fitPrecisionReplicate1 <- function(x){
  return(coefPrecision[1] + coefPrecision[2]*x + coefPrecision[4]*mean(MSEdataSample_IDReplicateIncubationExperience$Mean_Time_Sec))
}
fitPrecisionReplicate2 <- function(x){
  return(coefPrecision[1] + coefPrecision[2]*x + coefPrecision[3]+ coefPrecision[4]*mean(MSEdataSample_IDReplicateIncubationExperience$Mean_Time_Sec))
}
```
## Among observer repeatability
```{r }
## Mixed model
m0 <- lme4::lmer(log(Obs_No_Larvae+1)~1+(1|Sample_ID)+(1|Observer_ID), data=data, REML = TRUE)
summary(m0)

## Extract variance components
VAR <- as.data.frame(lme4::VarCorr(m0))$vcov

## Compute repeatability among observers
RepeatabilityAmong <- VAR[1]/sum(VAR)
## Compute repeatability within observers
RepeatabilityWithin <- VAR[1]/sum(VAR[c(1, 3)])
```

# Plots
```{r }

## Space between replicates
x <- 0.25
siz <- 10
linesize <- 0.5

## Relationship between bias and expected number of larvae
p2A <- MSEdataSample_IDReplicateIncubation %>%
  dplyr::mutate(True_No_Larvae=dplyr::if_else(Replicate==1, True_No_Larvae-x, True_No_Larvae+x)) %>%
  ggplot(aes(x=True_No_Larvae, y=Mean_Time_Sec, color=Replicate, shape=Incubation)) +
  geom_point() + xlim(-1, 35) + ylim(0, 125) +
  xlab("Exact number of larvae per fruit") + ylab("Time for counting larvae (sec.)") + scale_color_discrete(name = "Count replicate") +
  theme(text = element_text(size = siz)) + 
  geom_line(stat='function', fun=fitTimeReplicate1, color='#F8766D', linetype='solid', size=linesize) + 
  geom_line(stat='function', fun=fitTimeReplicate2, color='#00BFC4', linetype='solid', size=linesize) +
     scale_shape_manual(values = c(1, 16) ) 

p2A

## Relationship between bias and expected number of larvae
p2B <- MSEdataSample_IDReplicateIncubation %>%
  dplyr::mutate(True_No_Larvae=dplyr::if_else(Replicate==1, True_No_Larvae-x, True_No_Larvae+x)) %>%
  ggplot(aes(x=True_No_Larvae, y=Bias_Obs_No_Larvae, color=Replicate, shape=Incubation)) + geom_point() + xlim(-1, 35) + ylim(-20, 1) + xlab("Exact number of larvae per fruit") + ylab("Bias in larval count estimates") + scale_color_discrete(name = "Count replicate") + theme(text = element_text(size = siz))+ 
  geom_line(stat='function', fun=fitBiasIncubationYes, color='#F8766D', linetype='solid', size=linesize) + 
  geom_line(stat='function', fun=fitBiasIncubationNo, color='#F8766D', linetype='dotted', size=linesize)+ 
  geom_line(stat='function', fun=fitBiasIncubationYesReplicate2, color='#00BFC4', linetype='solid', size=linesize) + 
  geom_line(stat='function', fun=fitBiasIncubationNoReplicate2, color='#00BFC4', linetype='dotted', size=linesize)+
     scale_shape_manual(values = c(1, 16) )
p2B


## Relationship between variance and expected number of larvae
p2C <- MSEdataSample_IDReplicateIncubation %>%
  dplyr::mutate(True_No_Larvae=dplyr::if_else(Replicate==1, True_No_Larvae-x, True_No_Larvae+x)) %>%
  ggplot(aes(x=True_No_Larvae, y=SD_Obs_No_Larvae, color=Replicate, shape=Incubation)) + geom_point() + xlim(-1, 35) + ylim(0, 10) + xlab("Exact number of larvae per fruit") + ylab("Standard deviation \nin larval count estimates") + scale_color_discrete(name = "Count replicate") + theme(text = element_text(size = siz))+ 
  geom_line(stat='function', fun=fitPrecisionReplicate1, color='#F8766D', linetype='solid', size=linesize) + 
  geom_line(stat='function', fun=fitPrecisionReplicate2, color='#00BFC4', linetype='solid', size=linesize)+
  scale_shape_manual(values = c(1, 16) )
p2C


figure <- ggpubr::ggarrange(p2A, p2B, p2C,
                    labels = c("A", "B", "C"),
                    ncol = 1, nrow = 3, common.legend = TRUE, legend = "right")

title_plot <- "Fig2_TimeBiasSDbyNumLarvaeandReplicateIncubation.png"
cowplot::save_plot(file =here::here("plots", title_plot),
                 figure, base_height = 21/cm(1),
                  base_width = 10/cm(1), dpi = 1200)


```
# Supp. plots
```{r}

## Relationship between expected and observed number of larvae
pS1 <- data %>%
  dplyr::select(Obs_No_Larvae, True_No_Larvae, Incubation, Round) %>%
  ggplot(aes(x=True_No_Larvae, Obs_No_Larvae, color=Incubation)) + geom_point() + xlim(0, 35) + ylim(0, 35) + geom_abline(intercept = 0, slope = 1)+ xlab("Expected number of larvae") + ylab("Observed number of larvae") + scale_color_discrete(name = "48h-incubation")
pS1

title_plot <- "FigS1_Observed_Expected_No_Larvae.png"
cowplot::save_plot(file =here::here("plots", title_plot),
                 pS1, base_height = 10/cm(1),
                  base_width = 12.5/cm(1), dpi = 1200)



```
# Additional plots
## Time for counting larvae

```{r }
## Histogram with time
ggplot(data, aes(x=log(Time_Sec))) + 
  geom_histogram(binwidth=1)

siz <- 10
## Time used for counting as a function of number of larvae
p2A <- data %>%
  dplyr::mutate(Category_True_No_Larvae=cut(True_No_Larvae, breaks=c(0, 1, 6, Inf), labels=c("0","1-5","+5"), right = FALSE)) %>%
  dplyr::select(Category_True_No_Larvae, Incubation, Time_Sec) %>%
  ggplot(aes(x=Category_True_No_Larvae,  y=Time_Sec, color=Incubation)) + geom_boxplot() + xlab("Number of larvae") + ylab("Time for counting larvae (sec.)") + scale_color_discrete(name = "48h-incubation") + theme(text = element_text(size = siz))

p2A

```
## Accuracy (bias)
```{r }
p2B <- MSEdataSample_IDReplicateIncubation %>%
  dplyr::mutate(Category_True_No_Larvae=cut(True_No_Larvae, breaks=c(0, 1, 6, Inf), labels=c("0","1-5","+5"), right = FALSE)) %>%
  ggplot(aes(x=Category_True_No_Larvae, y=Bias_Obs_No_Larvae, color=Incubation)) + geom_boxplot() +
  xlab("Number of larvae") + ylab("Bias in larval count estimates") + scale_color_discrete(name = "48h-incubation") + theme(text = element_text(size = siz))
p2B
```

## Precision (standard deviation)
```{r }

p2C <- MSEdataSample_IDReplicateIncubation %>%
  dplyr::mutate(Category_True_No_Larvae=cut(True_No_Larvae, breaks=c(0, 1, 6, Inf), labels=c("0","1-5","+5"), right = FALSE)) %>%
  ggplot(aes(x=Category_True_No_Larvae, y=sqrt(Var_Obs_No_Larvae), color=Incubation)) + geom_boxplot() +
  xlab("Number of larvae") + ylab("Standard deviation in\n larval count estimates") + scale_color_discrete(name = "48h-incubation") + ylim(0, 7) + theme(text = element_text(size = siz))
p2C


figure <- ggpubr::ggarrange(p2A, p2B, p2C,
                    labels = c("A", "B", "C"),
                    ncol = 1, nrow = 3, common.legend = TRUE, legend = "bottom")
figure

```
# Test for differences in the number of larvae between incubated and non incubated samples
```{r}
## Check for an absence of differences in the number of larvae between incubated and non incubated samples

## Check the mean number of larvae for samples with 48h of incubation or not
truecounts %>%
  dplyr::group_by(Incubation) %>%
  dplyr::summarise(True_No_Larvae_mean=mean(True_No_Larvae), True_No_Larvae_median=median(True_No_Larvae))

m <- glm(True_No_Larvae~Incubation, data=truecounts, family="poisson")
summary(m)

```
